Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1231

%%%----Versions-----------------------------
% supclt1213.tex 2018/12/13 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{amsthm}
\usepackage{stackrel}
\usepackage[backref=section]{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

@@

    {CLT for Super-OU Processes with stable Branching}

@@

%\begin{abstract}
%\end{abstract}
%\keywords{}p
%\maketitle
%---Contents-----------------------

@@

    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$. For each testing function $f$ of at most polynomial growth,
    denote by $\kappa_f$ the order of $f$ in
the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.

@@

@@

\subsection{Model}\label{ss:1.1}
    Let $d \in \mathbb N:= \{1,2,\dots\}$ and
    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator

@@

        f \in C^2(\mathbb{R}^d),

@@

    where $\sigma>0$ and $b>0$ are constants.
    Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be the function on $\mathbb R_+:= [0,\infty)$ defined by
\begin{equation}\label{mechanism}
    \psi(z)
    := - \alpha z + z^{1+\beta},

@@

	where $\alpha > 0$ and $\beta \in (0,1) $ are constants.
    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite Borel measures on $\mathbb{R}^d$.
    For all Borel function $f$ and Borel measure $\mu$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.

@@

    We say an $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb{R}^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.

	The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.
    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
    Define
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x)
    :=
    e^{\alpha t} T_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle T_t^\alpha f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}

\subsection{OU Semigroup}
    In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
 %   For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$,
  For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
    let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    %p \in \mathbb{N}_0^{d}.
    p \in \mathbb{Z}_+^{d}.
\end{equation}
    It is known that $(T_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
    discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $A_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    Thus, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of the function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
%$
%	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|
%$
\begin{equation}\label{Q_k}
Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
\end{equation}
and
%$
%	Q f:= Q_{\kappa_f}f.
%$
\begin{equation}\label{Q}
Q f:= Q_{\kappa_f}f.
\end{equation}

    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
\subsection{}
    Let $X$ be the super OU-process discussed in Subsection \ref{ss:1.1}.
    Its branching mechanism $\psi$ can be extended to $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$:
 $$\psi(z) := -\alpha z + z^{1+\beta}, \quad z\in \mathbb C_+.$$
    According to the analysis in Subsection A.1,
    $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
   % Write $\psi_0(z) := \psi(z) + \alpha z$.
   Write $\psi_0(z) := \psi(z) + \alpha z=z^{1+\beta}$.
  %  Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
   Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}=(1+\beta)z^\beta$.
    For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$, the value of the L\'evy exponent of the infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}

@@

%For each $p\in \mathbb{N}_+^d$, we define
For each $p\in \mathbb{Z}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
   $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\mu\in \mathcal M_c(\mathbb R_d)$,
  thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for
any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$,
     as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$

>>>>

%%%----Versions-----------------------------
% supclt1213.tex 2018/12/13 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt,a4paper]{amsart}
	\setlength{\textwidth}{\paperwidth}
	\addtolength{\textwidth}{-2in}
	\calclayout
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
	\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
\usepackage[backref=section]{hyperref}
	\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
	\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{comment}
\usepackage{amsthm}
	\theoremstyle{plain}
	\newtheorem{thm}{Theorem}[section]
	\newtheorem{lem}[thm]{Lemma}
	\newtheorem{prop}[thm]{Proposition}
	\newtheorem{cor}[thm]{Corollary}
	\newtheorem{conj}[thm]{Conjecture}
	\theoremstyle{definition}
	\newtheorem{defi}[thm]{Definition}
	\newtheorem{rem}[thm]{Remark}
	\newtheorem{exa}[thm]{Example}
	\newtheorem{asp}{Assumption}
	\numberwithin{equation}{section}
	\allowdisplaybreaks

@@

    {\large CLT for Super-OU Processes with stable Branching}

@@

@@

    %Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$. 
    Consider a super-OU process $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, where $\alpha >0$ and $\beta\in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
$
    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}). 
$
    For each testing function $f$ of at most polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: 
    %In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
    In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly.
    %In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.
    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly.

@@

%\keywords{}

@@

\subsection{Model}
\label{ss:1.1}
	%Let $d \in \mathbb N:= \{1,2,\dots\}$ and
	Let $d \in \mathbb N:= \{1,2,\dots\}$. 
    %$\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator
    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with generator

@@

        f \in C^2(\mathbb R^d),

@@

    %where $a>0$ and $b>0$ are constants.
    where $a>0$ and $b>0$.
    %Denote by $(P_t^\alpha)_{t\geq 0}$ the transition semigroup of $\xi$.
    Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be the function on $\mathbb R_+$ defined by
\label{mechanism}
    %\psi(z)
    %:= - \alpha z + z^{1+\beta},
    \psi(x,z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy).

@@

	%where $\alpha > 0$ and $\beta \in (0,1) $ are constants.
	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
%added%
    Denote by $\mathcal B(\mathbb R^d)$ the space of all real-valued Borel measurable functions on $\mathbb R^d$.
%%end added%
	%For all Borel function $f$ and Borel measure $\mu$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
	For each $f\in \mathcal B(\mathbb R^d)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.

@@

    We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.
\end{equation}	
    The existence of superprocesses are well known, see \cite{Dynkin1993Superprocesses} for instance.

    According to the Subsection A.1, the branching mechanism $\psi$ can be extended on $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
 \[\psi(x,z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb C_+,\]
    which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
    \quad z\in \mathbb C_+.
\end{equation}

    \begin{asp}
\label{asp: branching mechanism}
    The branching mechanism takes the form of 
\[
    \psi(z) = -\alpha z + \eta z^{1+\gamma} + \psi_1(z),\quad z\in \mathbb C_+,
\]
    where $\eta > 0$, $\gamma \in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
\[
    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}),\quad z\in \mathbb C_+.
\]
\end{asp}

\begin{lem}
    Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$. 
    Also, $\psi$ satisfies the $L \log L$ critierion  i.e. 
\[
    \int_1^\infty y \log y~\pi(dr)< \infty.
\]
\end{lem}
\begin{proof}
    {\bf Need a proof.}
\end{proof}

    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\bar v \|\mu\|},
\end{equation}
    where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
    Define
\begin{equation}\label{meansemigroup}
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}

\subsection{OU Semigroup}
    In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb R^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
     For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
    let $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    p \in \mathbb{Z}_+^{d}.
\end{equation}
    It is known that $(P_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
    discrete spectrum $a(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $A_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{a}x \Big),
    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    P_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    Thus, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of the function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb R^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
\begin{equation}\label{Q_k}
Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|P_t f|,
\end{equation}
and
\begin{equation}\label{Q}
Q f:= Q_{\kappa_f}f.
\end{equation}
    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.

\subsection{complex valued FKPP equations}
    Let $X$ be the super OU-process introduced in Subsection \ref{ss:1.1}.    
   Write $\psi_0(z) := \psi(z) + \alpha z$,
   %Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}=(1+\beta)z^\beta$.
   and $\psi'_0(z) = \psi'(z) + \alpha$ for each $z\in \mathbb C_+$.
    For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$, the value of the L\'evy exponent of the infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{equation}\begin{split}
\label{eq:chareq2}
    U_tf(x)-\int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
    =i P^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{split}\end{equation}

@@

For each $p\in \mathbb{Z}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
  For any $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
   $L^{1+\gamma}(\mathbb{P}_{\mu})$.
  Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for
any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$,
     as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$

     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence. ({\bf In the proof of this theorem, where do we need the condition that $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$ ?})
 \end{thm}
For any $t\geq 0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$.
 \begin{rem}
Let $f \in \mathcal{P}$.  If $\kappa_f=0$,
    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},
for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$, as $t\rightarrow \infty$,
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence. ({\bf This result should be refered as the SLLN, right?})
 \end{rem}
